Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-09-03 journal paper/content/sim_details.tex
Added a para on the three classes.

\xhdr{MAB algorithms.} We consider the three classes of bandit algorithms discussed in Section~\ref{sec:intro-model} (and in more detail in Appendix~\ref{app:bg}), and look for qualitative differences between them. We take a representative algorithm from each class. Our pilot experiments indicate that our findings do not change substantially if other representative algorithms are chosen.
We use \Thompson (\TS) from the ``adaptive-exploration" algorithms, \DynamicEpsGreedy (\DEG) from the ``exploration-separating" algorithms,%
\footnote{In each round, \DynamicEpsGreedy algorithm explores uniformly with a predetermined probability $\eps$, and ``exploits" with the remaining probability, choosing an arm with maximal posterior mean reward given the current data. We use $\eps=5\%$ throughout. Our pilot experiments show that choosing a different $\eps$ does not qualitatively change the results.}  and \DynGreedy (\DG) algorithm  as in Section~\ref{sec:theory-prelims}. For ease of comparison, all three algorithms are parameterized with the same ``fake" Bayesian prior: namely, the mean reward of each arm is drawn independently from a $\Beta(1,1)$ distribution. Recall that Beta priors with 0-1 rewards form a conjugate family, which allows for simple posterior updates.

>>>>

\xhdr{MAB algorithms.} \asedit{We consider three essential classes of bandit algorithms: ones that never explicitly explore (\emph{greedy algorithms}), ones that explore without looking at the data (\emph{exploration-separating algorithms}), and ones where exploration gradually zooms in on the best arm (\emph{adaptive-exploration algorithms}). In the absence of competition, these classes are fairly well-understood: greedy algorithms are terrible for a wide variety of problem instances, exploration-separated algorithms learn at a reasonable but mediocre rate across all problem instances, and adaptive-exploration algorithms are optimal in the worst case, and exponentially improve for ``easy" problem instances (see Appendix~\ref{app:bg} for more details).}

We look for qualitative differences between these three classes. We take a representative algorithm from each class. Our pilot experiments indicate that our findings do not change substantially if other representative algorithms are chosen.
We use \Thompson (\TS) from the ``adaptive-exploration" algorithms, \DynamicEpsGreedy (\DEG) from the ``exploration-separating" algorithms,%
\footnote{In each round, \DynamicEpsGreedy algorithm explores uniformly with a predetermined probability $\eps$, and ``exploits" with the remaining probability, choosing an arm with maximal posterior mean reward given the current data. We use $\eps=5\%$ throughout. Our pilot experiments show that choosing a different $\eps$ does not qualitatively change the results.}  and \DynGreedy (\DG) algorithm  as in Section~\ref{sec:theory-prelims}. For ease of comparison, all three algorithms are parameterized with the same ``fake" Bayesian prior: namely, the mean reward of each arm is drawn independently from a $\Beta(1,1)$ distribution. Recall that Beta priors with 0-1 rewards form a conjugate family, which allows for simple posterior updates.
